### 2018-11-21 Chapters/Chapter3.tex
Stuffs
uni changes

In this chapter we will derive an effective Hamiltonian for different types of Hubbard-like models in the presence of a high frequency electromagnetic perturbation. The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately.

@@

In this case the hopping amplitudes are:

@@

\input{Chapters/SGraphene}

>>>>

In this chapter we will derive an effective Hamiltonian for different types of Hubbard-like models in the presence of a high frequency electromagnetic perturbation. The goal is to manipulate $J$ and $\bs{D}_{ij}$ in \ref{HeffNOEMF} separately. This has already been done for the case of Mott insulators (\cite{Mentink2015}, \cite{Kitamura2017}), in which only the exchange interaction $J$ plays a role.We reproduce the result, and extend the analysis to different systems with spin orbit interaction, thereby modulating $\bs{D}_{ij}$ or other spin interactions.

@@

The vector $\bs{\Delta}_{ij}$ can describe Rashba or Dresselhaus SOI, $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^y, -R_{ij}^x, 0)$ for Rashba SOI and $\bs{\Delta}_{ij} = i\Delta_R(R_{ij}^x, -R_{ij}^y, 0)$ for Dresselhaus SOI. 
In this case the hopping amplitudes are:

@@

\input{Chapters/KaneMele}
